\resheading{Work Experience}
\begin{itemize}[leftmargin=*]
  \item
        \ressubsingleline{\href{https://www.tencent.com/en-us/business/robotics.html}{Robotics X, Tencent}}{Robotics Engineer Intern}{2021.06 -- 2021.09}
        {\small
          \begin{itemize}
            \item Participated in a robotics control toolbox. The toolbox is written entirely in C++ and is designed for solving robot dynamics equations and model-based control planning problems. It has been successfully applied to Ollie, Jamoca and other robots.
          \end{itemize}
        }
  \item
        \ressubsingleline{\href{https://about.tmall.com/}{Tmall Group, Alibaba}}{Java Software Engineer Intern}{2018.07 -- 2018.09}
        {\small
          \begin{itemize}
            \item Design automated test software to protect against large-scale network traffic and potential DDOS attacks during the Double 11 festival.
            \item Provides an automated A/B testing environment leasing platform for more than ten business groups including Fliggy, Cainiao, Hema Fresh etc., covering more than 300 applications.
            \item Excellent project of Tmall technical department.
          \end{itemize}
        }
  \item
        \ressubsingleline{\href{https://www.neteasegames.com/}{Interactive Entertainment, NetEase}}{Game Designer Intern}{2018.09 -- 2018.12}
        {\small
          \begin{itemize}
            \item Design several game levels for a doomsday survival mobile game: LifeAfter. Also analyze game level map and character damage of Assassin's Creed Odyssey.
          \end{itemize}
        }
\end{itemize}